---
title: "Appendix"
author: "Joe Backer, Elle Dodd, Dan Humphrey, Dan Peckham"
date: "3/25/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	root.dir = "~/Documents/Stats2/pivotproject",
	tidy = TRUE)
```

```{r data}
library(haven)
library(sandwich)
library(stargazer)
library(ggplot2)
library(car)
library(knitr)
library(plyr)
library(lfe)
library(plm)
library(gtools)
```

``` {r data hygiene}
afghan <- read_dta("~/Documents/Stats2/pivotproject/afghandata.dta")
afghan <- rename(afghan, c("f07_hh_id"= "hh_id",
                 "f07_heads_child_cnt" = "heads_child",
                 "f07_girl_cnt" = "girl",
                 "f07_age_head_cnt" ="age_head",
                 "f07_yrs_ed_head_cnt" = "yrs_ed_head", 
                 "f07_jeribs_cnt" = "jeribs", 
                 "f07_num_sheep_cnt" = "num_sheep", 
                 "f07_duration_village_cnt" = "duration_village", 
                 "f07_farsi_cnt" = "farsi",
                 "f07_tajik_cnt" = "tajik", 
                 "f07_farmer_cnt"    = "farmer",
                 "f07_num_ppl_hh_cnt"   = "num_ppl_hh",
                 "f07_test_observed" = "test_observed",
                 "f07_formal_school" = "formal_school",
                 "f07_nearest_scl" = "nearest_scl",
                 
                 # non-matching new names#                 
                 "f07_age_cnt" = "age_child",
                 "f07_both_norma_total" = "test_score_normalized"
))
afghan$sheep_per_hh_member = afghan$num_sheep / afghan$num_ppl_hh
attach(afghan)
```

```{r Balance table}
#create data frame of only the variables of interest
remove <- c("hh_id", "observation_id")
varlist <- colnames(afghan[,!names(afghan) %in% remove])
balance_variables <-afghan[,!colnames(afghan) %in% remove]

#generate counts
n_treatment <- apply(balance_variables[balance_variables$treatment == 1,], 2, function(x) length(which(!is.na(x))))
n_control <- apply(balance_variables[balance_variables$treatment == 0,], 2, function(x) length(which(!is.na(x))))

#generate table
balancetable <-cbind(n_control,n_treatment)
#drop treatment row
balancetable<-balancetable[!rownames(balancetable) == "treatment", ]

#run t.tests, skipping treatment[14]
balance_tests <- lapply(varlist[c(1:13,15:20)], function(x) {
  t.test(as.formula(paste(x,"treatment",sep="~")), data = balance_variables, alternative = "two.sided", mu = 0, paired = FALSE, var.equal = FALSE, conf.level = 0.95)})

#extract and adjust p vals
balance_test_pvals <- t(sapply(balance_tests, function(x) {
  c(x$estimate[],
    "diff in means" =unname(x$estimate[1])-unname(x$estimate[2]),
    ci.lower = x$conf.int[1],
    ci.upper = x$conf.int[2],
    p.value = x$p.value,
    "adj.p.value" = p.adjust(x$p.value, method = "bonferroni", n = length(x)),
    x$parameter
  )
}))

balance_test_pvals <- data.frame(balance_test_pvals, stringsAsFactors=FALSE)
balance_test_pvals[] <- lapply(balance_test_pvals, function(x) as.numeric(as.character(x)))
balancetable<-cbind(balancetable,balance_test_pvals)
balancetable<-round(balancetable,3)
kable(balancetable)
```


```{r}

```


```{r}
kable(round(cor(afghan[,c("formal_school", "nearest_scl", "heads_child", "girl", "age_child", "age_head", "yrs_ed_head", "jeribs", "num_sheep", "duration_village", "farsi" ,"tajik" , "farmer","num_ppl_hh")]), digits = 2))
```

none are more than 0.35.
above magnitude 0.25 are:
yrs head of household education and farmer -0.28,
farsi and tajik -0.27,
duration in village and age of household head 0.3, 
sheep and jerobs 0.32.

```{r}
plot (afghan$jeribs, afghan$num_sheep)
plot (afghan$duration_village, afghan$age_head)
```

WHY CHOOSE PROBIT?
PLOT the RESIDUALS?
cross ref with balance tables
fixed effects for village

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
r1 <- lm(formal_school ~ nearest_scl, data = afghan)
r2 <- lm(formal_school ~ nearest_scl +  girl + age_child + age_head + num_sheep + jeribs + yrs_ed_head + heads_child+duration_village + num_ppl_hh + tajik + farsi ,  data = afghan)
r3 <- lm(formal_school ~ nearest_scl +  girl + age_child + age_head + num_sheep + jeribs + yrs_ed_head + heads_child+duration_village + num_ppl_hh + tajik + farsi + as.factor(clustercode), data = afghan)

p1 <- glm(formal_school ~ nearest_scl, data = afghan, family=binomial(link="probit"))
p2 <- glm(formal_school ~ nearest_scl +  girl + age_child + age_head + num_sheep + jeribs + yrs_ed_head + heads_child+duration_village + num_ppl_hh + tajik + farsi, data = afghan, family=binomial(link="probit"))
stargazer(r1, r2, r3, p1, p2,
          omit.stat = c("f", "ser", "aic", "ll"),
          intercept.bottom = FALSE,
          header=FALSE,
          summary=FALSE)
```

nearest_scl, girl, age_child, age_head, num_sheep all significant

```{r plot models against each other to compare predictions}
plot(predict(r2, type="response"), predict(p2, type="response"), xlab = "linear model", ylab = "probit model")
abline(a=0, b=1, col="red")
```

we can see the difference in the tails

```{r f test for language, wealth}
linearHypothesis(p2,c("tajik = 0","farsi = 0"),test="F")
linearHypothesis(p2,c("num_sheep = 0","jeribs = 0"),test="F")
```
jeribs and sheep jointly significant
farsi and tajik not.

---


```{r correlations, eval=FALSE, include=FALSE}
plot(afghan[,c("formal_school", "nearest_scl", "heads_child", "girl", "age_child", "age_head", "yrs_ed_head", "jeribs", "num_sheep", "duration_village", "farsi" ,"tajik" , "farmer","num_ppl_hh")])
```


```{r comparing glm and lm univariate models graphically, eval=FALSE, include=FALSE}
ggplot(afghan, aes(x=nearest_scl, y=formal_school)) + geom_point(shape=20) + geom_smooth(method=glm, method.args=list(family=binomial(link="probit")), se=FALSE) + geom_smooth(method=lm, se=FALSE, colour="red")
```


```{r}
detach(afghan)
```

